---
title: "Exploration SEM"
author: "Naisan Raji"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(LANG = "en")
```

### Load libraries

```{r libraries, warning=FALSE, message=FALSE}
require(tidyr) # pivot_wider()
require(dplyr) # select()
require(MatchIt)
require(lavaan)
# require(semPlot)
require(tidySEM) # plotting lavaan models
```

### Load data

```{r data}
# load("data/df") # takes super long to load, enable only when needed
load("data/df_trial") # trial-aggregated data
# df_trial <- df_trial[!is.na(df_trial$id),] # remove those rows
load("data/df_agg") # participant-aggregated data
load("data/demo_df.Rdata") # demographic data
```




# Preparation + Exploration
Merge datasets with demographic data:

```{r ar data}
# merge trial-aggregated data and demographic data
df_trial <- merge(df_trial, demo_df,
               by.x = c('pic', 'group', 'timepoint'),
               by.y = c('ID_Studie', 'group', 'timepoint'),
               all.x = T) # df_trial is main data frame
df_trial <- df_trial[!grepl('^9', df_trial$pic),] # keep only ASD data (remove IDs starting with 9)


df_agg <- merge(df_agg, demo_df,
               by.x = c('pic', 'group', 'timepoint'),
               by.y = c('ID_Studie', 'group', 'timepoint'),
               all.x = T) 
df_agg <- df_agg[!grepl('^9', df_agg$pic),]
```


Exclude trials 33 to 64.
```{r trials33-64}
df_trial <- df_trial[df_trial$trial %in% levels(df_trial$trial)[1:32], ]
```


Create `hit` variable
```{r hit prep}
# trial-level dataset
df_trial$hit <- !df_trial$missed_target # recode missed_target to hit by reversing all values

df_trial <- df_trial %>% # create variable with proportion of hits in relation to valid trials
  group_by(pic, timepoint) %>%
  mutate(hit_prop = mean(hit, na.rm = TRUE)) %>%
  ungroup()

# aggregated dataset:
df_agg$hit <- !df_agg$missed_target # recode missed_target to hit by reversing all values
```

Exclude trials with missing `time_to_target` and `time_to_target` shorter than 0.1 seconds.
```{r}
df_trial <- df_trial %>% na.omit(time_to_target) %>% filter(time_to_target >= 0.01)
df_agg <- df_agg %>% na.omit(time_to_target) %>% filter(time_to_target >= 0.01)
```


## Wide data: df_agg
Create wide data set for lavaan (aggregated data, conversion of trial-data is below):
```{r agg_wide}
# agg_wide <- df_agg %>% filter(group == "ASD") %>%
#   select(pic, timepoint, time_to_target, srs_total) %>%
#   pivot_wider(names_from = timepoint, 
#               names_glue = "{timepoint}_{.value}", 
#               values_from = c(time_to_target, srs_total))

agg_wide <- df_agg %>%
  select(pic, timepoint, time_to_target, hit_duration, hit, srs_total, rbsr:rbsr_cb) %>%
  pivot_wider(names_from = timepoint, 
              names_glue = "{timepoint}_{.value}", 
              values_from = c(time_to_target, hit_duration, hit, srs_total, rbsr:rbsr_cb))
```

## Wide data: df_trial

Trial-level data (time_to_target):
```{r ttt wide format}
timetotarget <- df_trial %>% select(pic, trial, timepoint, time_to_target, srs_total, rbsr:rbsr_cb)
timetotarget_t2 <- timetotarget %>% filter(timepoint == "T2") %>% select(-timepoint)
timetotarget_t4 <- timetotarget %>% filter(timepoint == "T4") %>% select(-timepoint)
timetotarget_t6 <- timetotarget %>% filter(timepoint == "T6") %>% select(-timepoint)
timetotarget_fu <- timetotarget %>% filter(timepoint == "FU") %>% select(-timepoint)
timetotarget_t2 <- timetotarget_t2 %>% rename_with(~ paste0("t2_", .), -c(pic, trial))
timetotarget_t4 <- timetotarget_t4 %>% rename_with(~ paste0("t4_", .), -c(pic, trial))
timetotarget_t6 <- timetotarget_t6 %>% rename_with(~ paste0("t6_", .), -c(pic, trial))
timetotarget_fu <- timetotarget_fu %>% rename_with(~ paste0("fu_", .), -c(pic, trial))

timetotarget <- merge(timetotarget_t2, timetotarget_t4, all = T)
timetotarget <- merge(timetotarget, timetotarget_t6, all = TRUE)
timetotarget <- merge(timetotarget, timetotarget_fu, all = TRUE)
rm(timetotarget_t2, timetotarget_t4, timetotarget_t6, timetotarget_fu) # remove from environment
```

Trial-level data (hit_duration):
```{r hit_dur wide format}
hit_dur <- df_trial %>% select(pic, trial, timepoint, hit_duration, srs_total, rbsr:rbsr_cb)
hit_dur_t2 <- hit_dur %>% filter(timepoint == "T2") %>% select(-timepoint)
hit_dur_t4 <- hit_dur %>% filter(timepoint == "T4") %>% select(-timepoint)
hit_dur_t6 <- hit_dur %>% filter(timepoint == "T6") %>% select(-timepoint)
hit_dur_fu <- hit_dur %>% filter(timepoint == "FU") %>% select(-timepoint)
hit_dur_t2 <- hit_dur_t2 %>% rename_with(~ paste0("t2_", .), -c(pic, trial))
hit_dur_t4 <- hit_dur_t4 %>% rename_with(~ paste0("t4_", .), -c(pic, trial))
hit_dur_t6 <- hit_dur_t6 %>% rename_with(~ paste0("t6_", .), -c(pic, trial))
hit_dur_fu <- hit_dur_fu %>% rename_with(~ paste0("fu_", .), -c(pic, trial))

hit_dur <- merge(hit_dur_t2, hit_dur_t4, all = T)
hit_dur <- merge(hit_dur, hit_dur_t6, all = TRUE)
hit_dur <- merge(hit_dur, hit_dur_fu, all = TRUE)
rm(hit_dur_t2, hit_dur_t4, hit_dur_t6, hit_dur_fu) # remove from environment
```

## Exploration time_to_target

From previous explorations, we know that the correlations between time_to_target (earlier timepoints with subsequent timepoints) are significant in the trial-wise data but not in the aggregated data. For exploration why that is, we explore the distributions:

```{r expl}
# T2
range(agg_wide$T2_time_to_target, na.rm = T)
range(timetotarget$t2_time_to_target, na.rm = T)
hist(agg_wide$T2_time_to_target)
hist(timetotarget$t2_time_to_target)

# T4
range(agg_wide$T4_time_to_target, na.rm = T)
range(timetotarget$t4_time_to_target, na.rm = T)
hist(agg_wide$T4_time_to_target)
hist(timetotarget$t4_time_to_target)

# T6
range(agg_wide$T6_time_to_target, na.rm = T)
range(timetotarget$t6_time_to_target, na.rm = T)
hist(agg_wide$T6_time_to_target)
hist(timetotarget$t6_time_to_target)

# FU2
range(agg_wide$FU_time_to_target, na.rm = T)
range(timetotarget$fu_time_to_target, na.rm = T)
hist(agg_wide$FU_time_to_target)
hist(timetotarget$fu_time_to_target)

# long data
range(df_trial$time_to_target, na.rm = T)
range(df_agg$time_to_target, na.rm = T)
hist(df_trial$time_to_target)
hist(df_agg$time_to_target)

# create a density plot for comparison of df_agg$time_to_target and df_trial$time_to_target
require(ggplot2)
# sreate df for plotting
df_plot <- data.frame(time_to_target = c(df_trial$time_to_target, df_agg$time_to_target),
                      df = rep(c("df_trial", "df_agg"), c(length(df_trial$time_to_target), length(df_agg$time_to_target)))
)

# Plot density plots
ggplot(df_plot, aes(x = time_to_target, fill = df)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density plot: time_to_target per df",
       x = "time_to_target",
       y = "Density") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "green"))

# T2
df_plot <- data.frame(time_to_target = c(timetotarget$t2_time_to_target, agg_wide$T2_time_to_target),
                      df = rep(c("timetotarget", "agg_wide"), 
                               c(length(timetotarget$t2_time_to_target), 
                                 length(agg_wide$T2_time_to_target))))

ggplot(df_plot, aes(x = time_to_target, fill = df)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density plot: time_to_target (T2)",
       x = "time_to_target",
       y = "Density") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "green"))

# T4
df_plot <- data.frame(time_to_target = c(timetotarget$t4_time_to_target, agg_wide$T4_time_to_target),
                      df = rep(c("timetotarget", "agg_wide"), 
                               c(length(timetotarget$t4_time_to_target), 
                                 length(agg_wide$T4_time_to_target))))

ggplot(df_plot, aes(x = time_to_target, fill = df)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density plot: time_to_target (T4)",
       x = "time_to_target",
       y = "Density") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "green"))

# T6
df_plot <- data.frame(time_to_target = c(timetotarget$t6_time_to_target, agg_wide$T6_time_to_target),
                      df = rep(c("timetotarget", "agg_wide"), 
                               c(length(timetotarget$t6_time_to_target), 
                                 length(agg_wide$T6_time_to_target))))

ggplot(df_plot, aes(x = time_to_target, fill = df)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density plot: time_to_target (T6)",
       x = "time_to_target",
       y = "Density") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "green"))

# FU2
df_plot <- data.frame(time_to_target = c(timetotarget$fu_time_to_target, agg_wide$FU_time_to_target),
                      df = rep(c("timetotarget", "agg_wide"), 
                               c(length(timetotarget$fu_time_to_target), 
                                 length(agg_wide$FU_time_to_target))))

ggplot(df_plot, aes(x = time_to_target, fill = df)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density plot: time_to_target (FU2)",
       x = "time_to_target",
       y = "Density") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "green"))
```

Questionable: Why are the ranges of time_to_target in the aggregated datasets wider than in the trial-wise datasets? Shouldn't that be the opposite?

## Exploration hit_duration
```{r expl hit_dur}
# long data
range(df_trial$hit_duration, na.rm = T)
range(df_agg$hit_duration, na.rm = T)
hist(df_trial$hit_duration)
hist(df_agg$hit_duration)

# create df for plotting
df_plot <- data.frame(hit_duration = c(df_trial$hit_duration, df_agg$hit_duration),
                      df = rep(c("df_trial", "df_agg"), c(length(df_trial$hit_duration), length(df_agg$hit_duration)))
)

# Plot density plots
ggplot(df_plot, aes(x = hit_duration, fill = df)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density plot: hit_duration per df",
       x = "hit_duration",
       y = "Density") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "green"))

```

The structure is about the same for the single timepoints (not shown here). Why is the variance much broader in the aggregated data?

# Path models

# No FU2

## SRS-16

### Time to target (trial data)

```{r ttt srs sem model}
model <- '# Regression paths
            t4_srs_total ~ ARa21 * t2_srs_total + CLb21 * t2_time_to_target
            t6_srs_total ~ ARa32 * t4_srs_total + CLb32 * t4_time_to_target + CL31 * t2_time_to_target
          
            t4_time_to_target ~ ARb21 * t2_time_to_target
            
            
          # Covariances
          t2_srs_total ~~ t2_time_to_target
          
          # Constrain FU covariances to zero
          '

model_fit <- sem(model = model, data = timetotarget, missing = "fiml") # default is listwise deletion which will result in no data, since there is no row without any NA!

lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_srs_total", "t4_srs_total", "t6_srs_total", "fu_srs_total",
                          "t2_time_to_target", "t4_time_to_target", "t6_time_to_target", "fu_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### Time to target (aggregated data)

```{r ttt srs agg, fig.width=10, fig.height=8}
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_time_to_target
            T6_srs_total ~ ARa32 * T4_srs_total + CLb32 * T4_time_to_target + CL31 * T2_time_to_target
            
            T4_time_to_target ~ ARb21 * T2_time_to_target
            
            
          # Covariances
          T2_srs_total ~~ T2_time_to_target
          '

model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000) # use wide format of aggregated visual search data
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

In both, the trial and aggregated data the model fit statistics are not interpretable (CFI/TLI higher than 1, RMSEA and SRMR very close to 0), but a main difference is the significant autoregression of time_to_target (T2) on time_to_target (T4) in the trial-data that we don't find in the aggregated data.

Prof. Freitag suggested scaling in different variations (Meeting 22.10.2024).

### Time to target (standardised agg data)

Aggregated data after scaling time_to_target (per timepoint):

```{r ttt srs agg scaled, fig.width=10, fig.height=8}
agg_wide_s <- agg_wide
agg_wide_s$T2_time_to_target <- scale(agg_wide_s$T2_time_to_target)
agg_wide_s$T4_time_to_target <- scale(agg_wide_s$T4_time_to_target)
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_time_to_target
            T6_srs_total ~ ARa32 * T4_srs_total + CLb32 * T4_time_to_target + CL31 * T2_time_to_target
            
            T4_time_to_target ~ ARb21 * T2_time_to_target
            
            
          # Covariances
          T2_srs_total ~~ T2_time_to_target
          '

model_fit <- sem(model = model, data = agg_wide_s, missing = "fiml", em.h1.iter.max=1000) # use wide format of aggregated visual search data
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```


Aggregated data after scaling time_to_target over all timepoints:

```{r ttt srs agg scaled2, fig.width=10, fig.height=8}
df_agg_s <- df_agg
df_agg_s$time_to_target <- scale(df_agg_s$time_to_target) # scale

# re-create agg_wide with scaled time_to_target
agg_wide_s <- df_agg_s %>%
  select(pic, timepoint, time_to_target, hit_duration, hit, srs_total, rbsr:rbsr_cb) %>%
  pivot_wider(names_from = timepoint, 
              names_glue = "{timepoint}_{.value}", 
              values_from = c(time_to_target, hit_duration, hit, srs_total, rbsr:rbsr_cb))

model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_time_to_target
            T6_srs_total ~ ARa32 * T4_srs_total + CLb32 * T4_time_to_target + CL31 * T2_time_to_target
            
            T4_time_to_target ~ ARb21 * T2_time_to_target
            
            
          # Covariances
          T2_srs_total ~~ T2_time_to_target
          '

model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000) # use wide format of aggregated visual search data
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Scaling does not make a difference in the non-significant autoregression between time_to_target T2 and T4.

### Hit duration (trial data)
```{r target fixation trial srs}
model <- '# Regression paths
            t4_srs_total ~ ARa21 * t2_srs_total + CLb21 * t2_hit_duration
            t6_srs_total ~ ARa32 * t4_srs_total + CLb32 * t4_hit_duration + CL31 * t2_hit_duration
            t4_hit_duration ~ ARb21 * t2_hit_duration
            
          # Covariances
          t2_srs_total ~~ t2_hit_duration'

model_fit <- sem(model = model, data = hit_dur, missing = "fiml")
varTable(model_fit) # plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_srs_total", "t4_srs_total", "t6_srs_total", "fu_srs_total",
                          "t2_hit_duration", "t4_hit_duration", "t6_hit_duration", "fu_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Model fit statistics not interpretable.


### Hit duration (aggregated data)
```{r target fixation agg srs}
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_hit_duration
            T6_srs_total ~ ARa32 * T4_srs_total + CLb32 * T4_hit_duration + CL31 * T2_hit_duration
            T4_hit_duration ~ ARb21 * T2_hit_duration
            
          # Covariances
          T2_srs_total ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)

```
Model fit statistics could be better, but they are interpretable and we observe a significant negative effect of `T2_hit_duration` on `T4_srs_total`.

## RBS-R total

### Time to target (trial data)
```{r ttt trial rbs total, fig.width=10, fig.height=8}
model <- '# Regression paths
            t4_rbsr ~ ARa21 * t2_rbsr + CLb21 * t2_time_to_target
            t6_rbsr ~ ARa32 * t4_rbsr + CLb32 * t4_time_to_target + CLb31 * t2_time_to_target
          
            t4_time_to_target ~ ARb21 * t2_time_to_target
            
          # Covariances
          t2_rbsr ~~ t2_time_to_target'

model_fit <- sem(model = model, data = timetotarget, missing = "fiml", em.h1.iter.max=2000)
varTable(model_fit) # okay, plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_rbsr", "t4_rbsr", "t6_rbsr", "fu_rbsr",
                          "t2_time_to_target", "t4_time_to_target", "t6_time_to_target", "fu_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

Model fit statistics indicate questionable fit but are at least interpretable (e.g. CFI/TLI smaller than 1)

### Time to target (aggregated data)
```{r ttt rbs total, fig.width=10, fig.height=8}
model <- '# Regression paths
            T4_rbsr ~ ARa21 * T2_rbsr + CLb21 * T2_time_to_target
            T6_rbsr ~ ARa32 * T4_rbsr + CLb32 * T4_time_to_target + CLb31 * T2_time_to_target
            T4_time_to_target ~ ARb21 * T2_time_to_target
            
          # Covariances
          T2_rbsr ~~ T2_time_to_target'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
varTable(model_fit) # okay, plausible
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr", "T4_rbsr", "T6_rbsr", "FU_rbsr",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Model fit statistics not interpretable.


### Hit duration (trial data)
```{r target fixation trial rbs}
model <- '# Regression paths
            t4_rbsr ~ ARa21 * t2_rbsr + CLb21 * t2_hit_duration
            t6_rbsr ~ ARa32 * t4_rbsr + CLb32 * t4_hit_duration + CL31 * t2_hit_duration
            t4_hit_duration ~ ARb21 * t2_hit_duration
            
          # Covariances
          t2_rbsr ~~ t2_hit_duration'

model_fit <- sem(model = model, data = hit_dur, missing = "fiml", em.h1.iter.max=2000)
varTable(model_fit) # plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_rbsr", "t4_rbsr", "t6_rbsr", "fu_rbsr",
                          "t2_hit_duration", "t4_hit_duration", "t6_hit_duration", "fu_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Fit measures interpretable, could be better, but significant effect of `T2_hit_duration` on `T6_rbsr`.

### Hit duration (aggregated data)

```{r target fixation agg rbs}
model <- '# Regression paths
            T4_rbsr ~ ARa21 * T2_rbsr + CLb21 * T2_hit_duration
            T6_rbsr ~ ARa32 * T4_rbsr + CLb32 * T4_hit_duration + CL31 * T2_hit_duration
            T4_hit_duration ~ ARb21 * T2_hit_duration
            
          # Covariances
          T2_rbsr ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr", "T4_rbsr", "T6_rbsr", "FU_rbsr",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Fit statistics not interpretable.

### RBS-R IS Hit duration
Aggregated data:
```{r target fixation agg rbs is}
model <- '# Regression paths
            T4_rbsr_is ~ ARa21 * T2_rbsr_is + CLb21 * T2_hit_duration
            T6_rbsr_is ~ ARa32 * T4_rbsr_is + CLb32 * T4_hit_duration + CL31 * T2_hit_duration
            T4_hit_duration ~ ARb21 * T2_hit_duration
            
          # Covariances
          T2_rbsr_is ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000)
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=2000)

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr_is", "T4_rbsr_is", "T6_rbsr_is", "FU_rbsr_is",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### RBS-R RSM Hit duration
Aggregated data:
```{r target fixation agg rbs rsm}
model <- '# Regression paths
            T4_rbsr_rsm ~ ARa21 * T2_rbsr_rsm + CLb21 * T2_hit_duration
            T6_rbsr_rsm ~ ARa32 * T4_rbsr_rsm + CLb32 * T4_hit_duration + CL31 * T2_hit_duration
            T4_hit_duration ~ ARb21 * T2_hit_duration
            
          # Covariances
          T2_rbsr_rsm ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000)
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=2000)

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr_rsm", "T4_rbsr_rsm", "T6_rbsr_rsm", "FU_rbsr_rsm",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### RBS-R SI Hit duration
Aggregated data:
```{r target fixation agg rbs si}
model <- '# Regression paths
            T4_rbsr_si ~ ARa21 * T2_rbsr_si + CLb21 * T2_hit_duration
            T6_rbsr_si ~ ARa32 * T4_rbsr_si + CLb32 * T4_hit_duration + CL31 * T2_hit_duration
            T4_hit_duration ~ ARb21 * T2_hit_duration
            
          # Covariances
          T2_rbsr_si ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000)
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=2000)

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr_si", "T4_rbsr_si", "T6_rbsr_si", "FU_rbsr_si",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### RBS-R CB Hit duration
Aggregated data:
```{r target fixation agg rbs cb}
model <- '# Regression paths
            T4_rbsr_cb ~ ARa21 * T2_rbsr_cb + CLb21 * T2_hit_duration
            T6_rbsr_cb ~ ARa32 * T4_rbsr_cb + CLb32 * T4_hit_duration + CL31 * T2_hit_duration
            T4_hit_duration ~ ARb21 * T2_hit_duration
            
          # Covariances
          T2_rbsr_cb ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000)
model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=2000)

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr_cb", "T4_rbsr_cb", "T6_rbsr_cb", "FU_rbsr_cb",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

# No VS autoregression

## SRS-16

### Time to target (trial data)

```{r ttt srs sem model no AR}
model <- '# Regression paths
            t4_srs_total ~ ARa21 * t2_srs_total + CLb21 * t2_time_to_target
            t6_srs_total ~ ARa32 * t4_srs_total + CL32 * t4_time_to_target + CL31 * t2_time_to_target
            
            
          # Covariances
          t2_srs_total ~~ t2_time_to_target
          '
model_fit <- sem(model = model, data = timetotarget, missing = "fiml", em.h1.iter.max=1000) # default is listwise deletion which will result in no data, since there is no row without any NA!

lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_srs_total", "t4_srs_total", "t6_srs_total", "fu_srs_total",
                          "t2_time_to_target", "t4_time_to_target", "t6_time_to_target", "fu_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Acceptable model fit statistics (mit Auge zudrücken...)

### Time to target (aggregated data)

```{r ttt srs agg no AR, fig.width=10, fig.height=8}
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_time_to_target
            T6_srs_total ~ ARa32 * T4_srs_total + CL32 * T4_time_to_target + CL31 * T2_time_to_target
            
          # Covariances
          T2_srs_total ~~ T2_time_to_target
          '

model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000) # use wide format of aggregated visual search data
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Model fit statistics not interpretable


### Hit duration (trial data)
```{r target fixation trial srs no AR}
model <- '# Regression paths
            t4_srs_total ~ ARa21 * t2_srs_total + CLb21 * t2_hit_duration
            t6_srs_total ~ ARa32 * t4_srs_total + CL32 * t4_hit_duration + CL31 * t2_hit_duration
            
          # Covariances
          t2_srs_total ~~ t2_hit_duration'

model_fit <- sem(model = model, data = hit_dur, missing = "fiml", em.h1.iter.max= 1000)
varTable(model_fit) # plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_srs_total", "t4_srs_total", "t6_srs_total", "fu_srs_total",
                          "t2_hit_duration", "t4_hit_duration", "t6_hit_duration", "fu_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Fit statistics not interpretable

### Hit duration (aggregated data)
```{r target fixation agg srs no AR}
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_hit_duration
            T6_srs_total ~ ARa32 * T4_srs_total + CL32 * T4_hit_duration + CL31 * T2_hit_duration
            
          # Covariances
          T2_srs_total ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```



## RBS-R total

### Time to target (trial data)
```{r ttt trial rbs total no AR, fig.width=10, fig.height=8}
model <- '# Regression paths
            t4_rbsr ~ ARa21 * t2_rbsr + CLb21 * t2_time_to_target
            t6_rbsr ~ ARa32 * t4_rbsr + CL32 * t4_time_to_target + CLb31 * t2_time_to_target
            
          # Covariances
          t2_rbsr ~~ t2_time_to_target'

model_fit <- sem(model = model, data = timetotarget, missing = "fiml", em.h1.iter.max=2000)
varTable(model_fit) # okay, plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_rbsr", "t4_rbsr", "t6_rbsr", "fu_rbsr",
                          "t2_time_to_target", "t4_time_to_target", "t6_time_to_target", "fu_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### Time to target (aggregated data)
```{r ttt rbs total no AR, fig.width=10, fig.height=8}
model <- '# Regression paths
            T4_rbsr ~ ARa21 * T2_rbsr + CLb21 * T2_time_to_target
            T6_rbsr ~ ARa32 * T4_rbsr + CL32 * T4_time_to_target + CLb31 * T2_time_to_target
            
          # Covariances
          T2_rbsr ~~ T2_time_to_target'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
varTable(model_fit) # okay, plausible
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr", "T4_rbsr", "T6_rbsr", "FU_rbsr",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```


### Hit duration (trial data)
```{r target fixation trial rbs no AR}
model <- '# Regression paths
            t4_rbsr ~ ARa21 * t2_rbsr + CLb21 * t2_hit_duration
            t6_rbsr ~ ARa32 * t4_rbsr + CL32 * t4_hit_duration + CL31 * t2_hit_duration
            
          # Covariances
          t2_rbsr ~~ t2_hit_duration'

model_fit <- sem(model = model, data = hit_dur, missing = "fiml", em.h1.iter.max=2000)
varTable(model_fit) # plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_rbsr", "t4_rbsr", "t6_rbsr", "fu_rbsr",
                          "t2_hit_duration", "t4_hit_duration", "t6_hit_duration", "fu_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
robust fit statistics indicate poor model fit (but are at least interpretable)

### Hit duration (aggregated data)

```{r target fixation agg rbs no AR}
model <- '# Regression paths
            T4_rbsr ~ ARa21 * T2_rbsr + CLb21 * T2_hit_duration
            T6_rbsr ~ ARa32 * T4_rbsr + CL32 * T4_hit_duration + CL31 * T2_hit_duration
            
          # Covariances
          T2_rbsr ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr", "T4_rbsr", "T6_rbsr", "FU_rbsr",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
fit statistics indicate very good model fit.

# Only T2 as predictor

## SRS-16

### Time to target (trial data)

```{r ttt srs sem model no t4}
model <- '# Regression paths
            t4_srs_total ~ ARa21 * t2_srs_total + CLb21 * t2_time_to_target
            t6_srs_total ~ ARa32 * t4_srs_total + CL31 * t2_time_to_target
            
            
          # Covariances
          t2_srs_total ~~ t2_time_to_target
          '
model_fit <- sem(model = model, data = timetotarget, missing = "fiml") # default is listwise deletion which will result in no data, since there is no row without any NA!

lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_srs_total", "t4_srs_total", "t6_srs_total", "fu_srs_total",
                          "t2_time_to_target", "t4_time_to_target", "t6_time_to_target", "fu_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### Time to target (aggregated data)

```{r ttt srs agg no t4, fig.width=10, fig.height=8}
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_time_to_target
            T6_srs_total ~ ARa32 * T4_srs_total + CL31 * T2_time_to_target
            
          # Covariances
          T2_srs_total ~~ T2_time_to_target
          '

model_fit <- sem(model = model, data = agg_wide, missing = "fiml", em.h1.iter.max=1000) # use wide format of aggregated visual search data
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```
Guter model fit!!! Sogar in den robusten fit statistics!


### Hit duration (trial data)
```{r target fixation trial srs no t4}
model <- '# Regression paths
            t4_srs_total ~ ARa21 * t2_srs_total + CLb21 * t2_hit_duration
            t6_srs_total ~ ARa32 * t4_srs_total + CL31 * t2_hit_duration
            
          # Covariances
          t2_srs_total ~~ t2_hit_duration'

model_fit <- sem(model = model, data = hit_dur, missing = "fiml")
varTable(model_fit) # plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_srs_total", "t4_srs_total", "t6_srs_total", "fu_srs_total",
                          "t2_hit_duration", "t4_hit_duration", "t6_hit_duration", "fu_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```


### Hit duration (aggregated data)
```{r target fixation agg srs no t4}
model <- '# Regression paths
            T4_srs_total ~ ARa21 * T2_srs_total + CLb21 * T2_hit_duration
            T6_srs_total ~ ARa32 * T4_srs_total + CL31 * T2_hit_duration
            
          # Covariances
          T2_srs_total ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_srs_total", "T4_srs_total", "T6_srs_total", "FU_srs_total",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```



## RBS-R total

### Time to target (trial data)
```{r ttt trial rbs total no t4, fig.width=10, fig.height=8}
model <- '# Regression paths
            t4_rbsr ~ ARa21 * t2_rbsr + CLb21 * t2_time_to_target
            t6_rbsr ~ ARa32 * t4_rbsr + CLb31 * t2_time_to_target
            
          # Covariances
          t2_rbsr ~~ t2_time_to_target'

model_fit <- sem(model = model, data = timetotarget, missing = "fiml", em.h1.iter.max=2000)
varTable(model_fit) # okay, plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_rbsr", "t4_rbsr", "t6_rbsr", "fu_rbsr",
                          "t2_time_to_target", "t4_time_to_target", "t6_time_to_target", "fu_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### Time to target (aggregated data)
```{r ttt rbs total no t4, fig.width=10, fig.height=8}
model <- '# Regression paths
            T4_rbsr ~ ARa21 * T2_rbsr + CLb21 * T2_time_to_target
            T6_rbsr ~ ARa32 * T4_rbsr + CLb31 * T2_time_to_target
            
          # Covariances
          T2_rbsr ~~ T2_time_to_target'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")
varTable(model_fit) # okay, plausible
summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr", "T4_rbsr", "T6_rbsr", "FU_rbsr",
                          "T2_time_to_target", "T4_time_to_target", "T6_time_to_target", "FU_time_to_target", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```


### Hit duration (trial data)
```{r target fixation trial rbs no t4}
model <- '# Regression paths
            t4_rbsr ~ ARa21 * t2_rbsr + CLb21 * t2_hit_duration
            t6_rbsr ~ ARa32 * t4_rbsr + CL31 * t2_hit_duration
            
          # Covariances
          t2_rbsr ~~ t2_hit_duration'

model_fit <- sem(model = model, data = hit_dur, missing = "fiml", em.h1.iter.max=2000)
varTable(model_fit) # plausible
lavInspect(model_fit, "coverage")
summary(model_fit, fit.measures = T)

model_graph <- get_layout("t2_rbsr", "t4_rbsr", "t6_rbsr", "fu_rbsr",
                          "t2_hit_duration", "t4_hit_duration", "t6_hit_duration", "fu_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```

### Hit duration (aggregated data)

```{r target fixation agg rbs no t4}
model <- '# Regression paths
            T4_rbsr ~ ARa21 * T2_rbsr + CLb21 * T2_hit_duration
            T6_rbsr ~ ARa32 * T4_rbsr + CL31 * T2_hit_duration
            
          # Covariances
          T2_rbsr ~~ T2_hit_duration'

model_fit <- sem(model = model, data = agg_wide, missing = "fiml")

summary(model_fit, fit.measures = T)

model_graph <- get_layout("T2_rbsr", "T4_rbsr", "T6_rbsr", "FU_rbsr",
                          "T2_hit_duration", "T4_hit_duration", "T6_hit_duration", "FU_hit_duration", rows = 2)
graph_sem(model = model_fit, layout = model_graph)
```


